### 2020-11-21 chatbot_classification/naacl_2021/experiments.tex
upload ver01

\subsection{Baselines}
We choose three kinds of system to construct our baselines.

@@

@@

The joint training does not improve the classification performance in stage 1,
measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
candidate  class  labels.  It  can  be  explained that, a classification model
inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
pair similairity model in the joint SFC poses more positive effect in optimizing the 
candidate labels.

>>>>

\subsection{Baselines}
We choose three kinds of system to construct our baselines. All our pretrained 
model baselines are being fine-tuned on all the experimental datasets. Additionally, 
the similarity model baseline will use the same fine-tuning process on Quora dataset  \cite{iyer2017first} as all our SFC models. As our researched problem is the application without sufficient data, the similarity model baseline is influenced due to insufficient in-domain data to a great extent. Thus, generally the similarity model baseline has to use external data.

@@

As for the training time, in our settings, our joint SFC model needs about 14
hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
needs about 12 hours, which indicates that our joint SFC model spends less training
time than the summation of two baseline models due to faster convergence.

As for the inference time, the classification model baseline is about 0.2 ms;
the similarity model baseline is about 0.5 ms and our joint SFC model takes only 0.6 ms.
Actually both the similarity model baseline and our joint SFC can be GPU
parallelized in the similarity computation, if we need pretty fast response time
in a real product.

@@

The joint training does not improve the classification performance in stage 1,
measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
candidate  class  labels, which can further improve the effect of sentence pair
similarity training. The reason is that, a classification model
inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
pair similairity model in the joint SFC poses more positive effect in optimizing the 
candidate labels.

### 2020-11-21 chatbot_classification/naacl_2021/introduction.tex
paper code for naacl
upload ver01

The  above  limitations motivate us to propose a joint system that is capable of
taking  advantages  from both the classification and similarity models. We call
it  as SFC,  short  for  similarity model fused with classification model, shown in
Fig.  \ref{fig:framework}.  We further bring in multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi} to train SFC.  
Our basic  idea  consists of two stages. In the first stage, we use an auxiliary model
to  select  top-K most possible labels for an input. This model can be an elastic
search  \cite{divya2013elasticsearch}  or a text classification model trained on
current   task-specific   chatbot   data.  In  the  second  stage,  we  build  a
classification  model  whose  main  modules  are  similarity  models. Then, this
structure  derives  two  goals to train towards, the classification loss for our
application,  and  the similarity loss for the main modules. When the two stages
are  independently optimized, we call \emph{two-stage SFC}. We further find that
the  quality of the output from the first stage might limit the final performance of the
system,  since  the  candidate labels for each user query is always fixed in the
whole  multi-task  training  process.  This  observation motivates us to further
improve  the  two-stage  SFC  into a joint training setting, called \emph{joint SFC}. In
this  way,  the  candidate texts associated  with the top-K classes also become
dynamic,  and  the  text  classification  model  in the first stage will also be
further optimized to provide better top-K results by the final training loss.

@@

\begin{figure*}[t]
  \begin{centering}
    \includegraphics[scale=0.72]{picture/picture4} 
    \par
  \end{centering}
  \caption{
    \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
    the  same  network  from  stage  1  and  stage 2, with the only difference
    whether two stages being jointly trained.
  }
  \label{fig:framework}
\end{figure*}

>>>>

The  above  limitations motivate us to propose a joint system that is capable of
taking  advantages  from both the classification and similarity models. The similarity
model can help us involve the data augmentation method to overcome the data insufficiency
challenge. In the meantime, the candidate labels provided by classification model can 
effectively reduce the noise for sentence pair semantic similarity task. We call
our system as SFC,  short  for  similarity model fused with classification model, shown in
Fig.  \ref{fig:framework}.  We further bring in multi-task learning   \cite{caruana1993multitask,collobert2008unified,  liu2019multi} to train SFC.  
Our basic  idea  consists of two stages. In the first stage, we use an auxiliary model
to  select  top-K most possible labels for an input. This model can be an elastic
search  \cite{divya2013elasticsearch}  or a text classification model trained on
current   task-specific   chatbot   data.  In  the  second  stage,  we  build  a
classification  model  whose  main  modules  are  similarity  models. Then, this
structure  derives  two  goals to train towards, the classification loss for our
application,  and  the similarity loss for the main modules. When the two stages
are  independently optimized, we call \emph{two-stage SFC}. We further find that
the  quality of the output from the first stage might limit the final performance of the
system,  since  the  candidate labels for each user query is always fixed in the
whole  multi-task  training  process.  This  observation motivates us to further
improve  the  two-stage  SFC  into a joint training setting, called \emph{joint SFC}. In
this  way,  the  candidate texts associated  with the top-K classes also become
dynamic,  and  the  text  classification  model  in the first stage will also be
further optimized to provide better top-K results by the final training loss.

@@

\begin{figure*}[t]
  \begin{centering}
    \includegraphics[scale=0.66]{picture/picture4} 
    \par
  \end{centering}
  \caption{
    \textbf{Network Structure of SFC:} two-stage SFC and joint-SFC are sharing
    the  same  network  from  stage  1  and  stage 2, with the only difference
    whether two stages being jointly trained.
  }
  \label{fig:framework}
\end{figure*}

### 2020-11-21 chatbot_classification/naacl_2021/related_work.tex
upload ver01

Another   line   of   interesting   work  is  the  joint  training  of  sentence
classification     and     NER,     such    as    
\cite{kruengkrai2020improving,zhang2020graph,hakkani2016multi,liu2016attention,goo2018slot}.  
For  example,  If  both  the  city and date information are
recognized,  then  they  are good indicators that this query might be booking an
ticket.

>>>>

Another   line   of   interesting   work  is  the  joint  training  of  sentence
classification     and     NER,     such    as    
\cite{kruengkrai2020improving,zhang2020graph,hakkani2016multi,liu2016attention,goo2018slot}.  
For  example,  If  both  the  city and date information are
recognized,  then  they  are good indicators that this query might be booking an
ticket. Considering a joint model, our framework is supportive of NER
training using the same method as mentioned in \cite{chen2019bert}. 
However in our case, the four public datasets and one private dataset we are using
do not have any NER information. Thus, in this work, we exclusively compare the classification
performance.
